% VDE Template for EUSAR Papers
% Provided by Barbara Lang und Siegmar Lampe
% University of Bremen, January 2002
% English version by Jens Fischer
% German Aerospace Center (DLR), December 2005
% Additional modifications by Matthias Wei{\ss}
% FGAN, January 2009

%-----------------------------------------------------------------------------
% Type of publication
\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------------------------
% Other packets: Most packets may be downloaded from www.dante.de and
% "tcilatex.tex" can be found at (December 2005):
% http://www.mackichan.com/techtalk/v30/UsingFloat.htm
% Not all packets are necessarily needed:
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
%\usepackage{ngerman} % in german language if required
\usepackage[nooneline,bf]{caption} % Figure descriptions from left margin
\usepackage{times}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{epsfig}
\usepackage{url}
\usepackage{framed}

\input{tcilatex}
%-----------------------------------------------------------------------------
% Page Setup
\textheight24cm \textwidth17cm \columnsep6mm
\oddsidemargin-5mm                 % depending on print drivers!
\evensidemargin-5mm                % required margin size: 2cm
\headheight0cm \headsep0cm \topmargin0cm \parindent0cm
\pagestyle{empty}                  % delete footer and header
%----------------------------------------------------------------------------
% Environment definitions
\newenvironment*{mytitle}{\begin{LARGE}\bf}{\end{LARGE}\\}%
\newenvironment*{mysubtitle}{\bf}{\\[1.5ex]}%
\newenvironment*{myabstract}{\begin{Large}\bf}{\end{Large}\\[2.5ex]}%
%-----------------------------------------------------------------------------
% Using Pictures and tables:
% - Instead "table" write "tablehere" without parameters
% - Instead "figure" write "figurehere " without parameters
% - Please insert a blank line before and after \begin{figuerhere} ... \end{figurehere}
%
% CAUTION:   The first reference to a figure/table in the text should be formatted fat.
%
\makeatletter
\newenvironment{tablehere}{\def\@captype{table}}{}
\newenvironment{figurehere}{\def\@captype{figure}\vspace{2ex}}{\vspace{2ex}}
\newcounter{CLCounter}
\newenvironment{CLCode}
{%
	\footnotesize\begin{framed}%
    \refstepcounter{CLCounter}%
  \textbf{OpenCL Reference \arabic{CLCounter}\\}%
  \quad
}
{%
\end{framed}%
}
\makeatother



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\nocite{*}
% Please use capital letters in the beginning of important words as for example
\begin{mytitle}INTRODUCTION TO OPENCL AND DEVICE FISSION\end{mytitle}
\begin{mysubtitle}\end{mysubtitle}
%
% Please do not insert a line here
%
\\
Arnaboldi Gabriele\\
Matr. 765568, (arnaboldi@libero.it)\\
\hspace{10ex}
\begin{flushright}
\emph{Report for the master course of Embedded Systems}\\
\emph{Reviser: PhD. Patrick Bellasi (bellasi@elet.polimi.it)}
\end{flushright}

Received: January, 11 2014\\
\hspace{10ex}

\begin{myabstract} Abstract \end{myabstract}
{\footnotesize
Over the past years, parallel computation has emerged as one of the most promising paradigms for achieving higher performances and, thanks to their architecture, modern graphics adapters revealed to be the best choice to implement such applications.
As a token of this claim, various GPGPU APIs and programming framework has been publicly released in the last years, and OpenCL is one of the most interesting and versatile of them.
The goal of this report is to first provide a general idea on what GPU computing is and then to analyze how the OpenCL model works and how a basic OpenCL application should be implemented. After the basic concepts have been sorted out, we'll move on a more advanced concept, that is Device Fission.
Device Fission allows the programmer to create many different subdevices and to have total control over hardware resources, this can be very useful when resources are limited, for example when working on embedded environments. To better describe how Device Fission works, we'll present five different scenarios in which it can be applied.
To conclude this report we'll present some interesting examples of real world OpenCL application and studies.}

\vspace{4ex}	% Please do not remove or reduce this space here.
\begin{multicols}{2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{Sect_01}
\input{Sect_02}
\input{Sect_03}
\input{conclusions}
\end{multicols}
\appendix
\input{Appendix_A}
\input{Appendix_B}
\begin{multicols}{2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% We suggest the use of JabRef for editing your bibliography file (Report.bib)
\bibliographystyle{splncs}
\bibliography{Report}

\end{multicols}
\end{document}
